The previous two chapters discussed methods that enable automatic content classification, and that address tag sparsity of annotated online content. This chapter studies a specific type of personalization system, namely a recommendation system, and shows how it can be designed for enterprise ecosystem, as well as how it can be made efficient and hence scalable. 


  Enterprise knowledge workers have been overwhelmed by the growing
  rate of incoming data in recent years.  In this chapter, we present a
  recommendation system with the goal of helping knowledge workers in
  discovering useful new content.  Specifically, our system builds
  personalized user models based on file activities on enterprise
  network file servers.  Our models use novel features that are
  derived from file metadata and user collaboration.  Through
  extensive evaluation on real world enterprise data, we demonstrate
  the effectiveness of our system with high precision and recall
  values.  Unfortunately, our experiments reveal that per-user models
  are unable to handle heavy workloads.  To address this
  limitation, we propose a novel optimization technique, Active
  Feature-based Model Selection, that predicts the user models that 
should be applied on each test file. Such a technique can reduce the 
classification time per file by as much as 23 times without sacrificing accuracy. 

  We also show how this technique can be extended to improve the
  scalability exponentially at marginal cost of prediction accuracy, e.g., we can 
 gain 169 times faster performance on average across all shares by sacrificing 4\%
  of F-score.

%% Input other tex files. Begin. %% 
\input{FileAccess/intro.tex}
\input{FileAccess/overallsystem.tex}
\input{FileAccess/evaluation.tex} 
\input{FileAccess/motivationSpeedup.tex}
\input{FileAccess/testspeedup.tex} 
%\input{deployment.tex} 
\input{FileAccess/relwork.tex}
\input{FileAccess/conclusion.tex}

